---
title: "ca_map"
author: Isbaelle Foster
output: Maps & Analysis

#references: https://rdrr.io/cran/tigris/man/counties.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown is for the purposes of generating a map of CA.
```{r echo=FALSE}
# Libraries
library(tidyverse)
library(tidycensus)
library(leaflet)
library(leaflet.extras)
library(dplyr)
library(sf)
library(maps)
library(tigris)
library(ggplot2)
library(lubridate)
library(RColorBrewer)
library(ussf)
library(viridis)

# PARAMETERS

# Read in Files and Data

file_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/ca-data.rds") 
amz_wmt_zip_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/amz_wmt_zip.rds") 

##This is using the updated snap_reach file from Sam, updated for 2019
amz_wmt_reach_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/snap_reach.rds") 

ruccodes <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data-raw/ruralurbancodes2013-3.csv")

#Colors

COLOR_LOW = "darkorchid1"
COLOR_HIGH = "darkorchid4"
```

# Read in Data

```{r}
ca_data <- 
  read_rds(file_in) %>%
  mutate(fips = as.integer(fips))
amz_wmt_zip <- read_rds(amz_wmt_zip_in)
amz_wmt_reach <- read_rds(amz_wmt_reach_in)
ruc_codes <- read_csv(ruccodes)
ca_zip <- read_rds("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/ca_zip.rds")

```

# Read in Geometry Shape File

```{r}
ca_counties <- 
  ussf::boundaries(
    geography = "county",
    resolution = "5m", 
    projection = "longlat"
  ) %>%
  filter(as.integer(STATEFP) == 06) %>%
  mutate(fips = as.integer(GEOID))
  
```

## Create Column for Number of Cases, by Month

```{r}
df <- 
  ca_data %>% 
  select(date, fips, cases, deaths) %>%
  mutate(cases = as.integer(cases)) %>%
  mutate(
    date = as.Date(date), 
    month = month(date)
  ) %>%
  group_by(fips, month) %>%
  summarise(total = sum(cases))

```

# Work with Bill
#Imp. note to create a floor on the date, so that there aren't duplicate years
```{r}
# ca_cases <-
#   ca_counties %>%
#   left_join(
#     ca_data %>%
#       mutate(month = lubridate::floor_date(date, unit = "month")) %>%
#       group_by(fips, month) %>% 
#       summarize(total = sum(cases)) %>%
#       ungroup() %>%
#       left_join(ca_pop, by = "fips") %>%
#       mutate(cases_per_capita = total / pop),
#     by = "fips"
#   )
# 
# ca_walmart <-
#   amz_wmt_zip$wmt_zip %>%
#   st_as_sf() %>%
#   st_transform(crs = st_crs(4326))
# 
# ca_amazon <-
#   amz_wmt_zip$amz_zip %>%
#   st_transform(crs = 4326)
```


##ggplot with Bill
```{r}

# ggplot() +
#   #geom_sf(aes(fill = cases_per_capita), data = ca_cases) +
#  # geom_sf(aes(fill = area), data = st_as_sf(amz_wmt_zip$wmt_zip)) 
#   geom_sf(data = amz_wmt_zip$wmt, color = "red")

```


# Create Fips Variable for ca_counties

```{r}

ca_counties <-
  ca_counties %>%
  mutate(fips = as.integer(GEOID))

```

# Join Data Sets

```{r}

df <-
  df %>%
  left_join(ca_counties, by = "fips")

```


## Get County Data from Census Data 

```{r}

census_ca <-
  load_variables(year = 2019, dataset = "acs5")

vars_acs5 <-
  c(
    total_pop = "B01003_001",
    total_HH = "B19058_001",
    total_SNAP = "B19058_002", 
    total_white = "B02001_002",
    total_black = "B02001_003",
    total_nativeAlaska_AmInd = "B02001_004",
    total_asian = "B02001_005",
    total_Haw_PacIs = "B02001_006",
    total_other = "B02001_007",
    total_twoMore = "B02001_008",
    total_latino = "B03001_003",
    has_comp = "B28003_002",
    has_comp_dialUp = "B28003_003",
    has_comp_broadband = "B28003_004",
    has_comp_noInternet = "B28003_005",
    no_internet = "B28002_013",
    no_comp = "B28003_006",
    workTransVehicle = "B08301_002",
    workTransPublicTrans = "B08301_010",
    workTrans_bike = "B08301_018",
    workTrans_walk = "B08301_019",
    workTrans_other = "B08301_020",
    workTrans_workHome = "B08301_021"
  )

df_acs5 <-
  get_acs(
    geography = "county",
    variables = vars_acs5,
    year = 2019,
    state = 06
  )

# ##added with Bill 
# ca_pop <-
#   get_acs(
#     geography = "county",
#     variables = "B01003_001",
#     year = 2018,
#     state = 06
#   ) %>%
#   transmute(
#     fips = as.integer(GEOID),
#     pop = estimate
#   )


```

## Join Census Data to COVID data, using FIPS

```{r}

# Create FIPS variable in ACS data frame

df_acs5 <-
  df_acs5 %>%
    mutate(
      fips = as.integer(GEOID)
    )

# Left join data COVID data set and create new variables per population count

df_allVar <-
  df %>%
  left_join(df_acs5, by = "fips") %>%
  select(-moe) %>%
  #ungroup() %>% 
  pivot_wider(
    names_from = variable,
    values_from = estimate
  ) %>%
  mutate(
    cases_perPop = (total / total_pop),
    percentWhite = (total_white / total_pop),
    percentBlack = (total_black / total_pop),
    percentNative = (total_nativeAlaska_AmInd / total_pop),
    percentAsian = (total_asian / total_pop),
    percentHaw_PacI = (total_Haw_PacIs / total_pop),
    percentOther = (total_other / total_pop),
    percentTwoMore = (total_twoMore / total_pop),
    percent_Latino = (total_latino / total_pop),
    percent_trans_vehicle = (workTransVehicle / total_pop),
    percentTransPublic = (workTransPublicTrans / total_pop),
    percentTransBike = (workTrans_bike / total_pop),
    percentTransWalk = (workTrans_walk / total_pop),
    percentTransOther = (workTrans_other / total_pop),
    percentTransHome = (workTrans_workHome / total_pop),
    percentSnap = (total_SNAP / total_HH),
    percentComp = (has_comp / total_pop),
    percentDialUp = (has_comp_dialUp / total_pop),
    percentBroadband = (has_comp_broadband / total_pop),
    percentNoInternet = (no_internet / total_pop),
    percentNoComp = (no_comp / total_pop)
  )
 

# Making this df to test/compare number of SNAP HH/total HH

df_allVar_test <-
  df_allVar %>%
  select(total_HH, total_SNAP, month) %>%
  filter(month == 8)

sum(df_allVar_test$total_SNAP)
sum(df_allVar_test$total_HH)

```


# Read RUC Code Data as numberics

```{r}
ruc_codes 
  ruc_codes$FIPS <- as.numeric(ruc_codes$FIPS)
  ruc_codes$RUCC_2013 <- as.numeric(ruc_codes$RUCC_2013)
 

```


# Join RUC Code Data
```{r}
#ruc_codes_new <-
#ruc_codes %>%
# rename(
# fips = FIPS)
  
colnames(ruc_codes) <- c("fips","State","County_Name", "Population_2010", "RUCC_2013", "Description")

df_allVar2 <-
  df_allVar %>%
    left_join(ruc_codes, by = "fips")

```


## Create Plot of CA
## Used this site as reference: https://rdrr.io/cran/tigris/man/counties.html

```{r}
# ca <- counties("California", cb = TRUE)
# 
# gg <- ggplot()
# gg <- gg + geom_sf(data = ca, color="black", fill = "white", size=0.25)
# 
# gg
```


## Create HeatMap of CA with Total Number of COVID Cases for the Month of July 2020

```{r}

df %>% 
  st_as_sf() %>%  
  filter(month == 6) %>% 
  ggplot() +
  geom_sf(aes(fill = total), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Total COVID CA Cases Per Month, June 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )

# df %>%
#   filter(month==7) %>%
#   View()

```

## Create Heat Map of CA with Cases Count per Population for June 2020

```{r}

 df_allVar %>%
  st_as_sf() %>%  
  filter(month == 6) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, June 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )



```

```{r}
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )

```



## Map with Sam Overlap

```{r}
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )



```



## Create Heat Maps of CA for Transportation
```{r}

# Map for Vehicle as Main Transportation Form
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percent_trans_vehicle), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Transportion to Work, Vehicle",
    caption = "Source: ACS 2019 Census Data"
  )

# Map for Public Transport as Main Transportation Form
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = workTransPublicTrans), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Transportion to Work, Public Transit",
    caption = "Source: ACS 2019 Census Data"
  )

```

## Map for SNAP Usage

```{r}

# Map for SNAP Usage
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentSnap), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population on SNAP",
    caption = "Source: ACS 2019 Census Data"
  )
```

## Map of Computer Usage & Internet Access

```{r}

# Map for Computer Access
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentComp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Computer Access",
    caption = "Source: ACS 2019 Census Data"
  )

# Map for Dial Up

df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentDialUp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Dial Up",
    caption = "Source: ACS 2019 Census Data"
  )


# Map for Broadband
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentBroadband), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Broadband",
    caption = "Source: ACS 2019 Census Data"
  )

```


## Map of No Internet / No Computer Access

```{r}

# Map for No Internet

df_allVar %>%
  st_as_sf() %>%  
  #filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentNoInternet), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Internet",
    caption = "Source: ACS 2019 Census Data"
  )

# Map for No Computer

df_allVar %>%
  st_as_sf() %>%  
  #filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentNoComp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Computer",
    caption = "Source: ACS 2019 Census Data"
  )




```


# Create Data Tables for Initial Exploratory Comparison

```{r}
# ca_counties <-
#   ca_counties %>%
#   rename(County = "NAME")
# 
# amz_wmt_reach %>%
#   rename(County = "NAME")

exploratory <-
  amz_wmt_reach %>%
    left_join(ca_counties %>% select(NAME, fips), by = "NAME")

# exploratory <-
#   exploratory[,-8] %>%
#  # rename(fips = "county")
#   #mutate('fips' = as.numeric(exploratory$county) + 6000)
  

# Join with RUC codes

exploratory <-
  exploratory %>%
  left_join(ruc_codes %>% select(fips, RUCC_2013), by = "fips")

exploratory <-
  exploratory %>%
  left_join(df_allVar2 %>% select(fips, cases_perPop, month, total_pop, total_SNAP, total_HH), by = "fips")

#plot(x=exploratory$RUCC_2013, y=exploratory$`SNAP Concentration`, type="p")

# Graph w/ Labels
ggplot(exploratory) +
  geom_point(aes(x = RUCC_2013, y = `% Reached`)) +
  ggtitle("SNAP Coverage and Rurality") +
  #geom_text(aes(x=RUCC_2013,y=`% Reached`, label=County, vjust = 0, hjust = 0))
  geom_text(aes(x = RUCC_2013, y =`% Reached`, label = NAME))

# Graph w/o Labels
ggplot(exploratory, aes(x=RUCC_2013, y =`% Reached`))+
  geom_point(shape = 1)

```

```{r}
# Calculate Statistics on Lack of Rural Coverage

# SNAP Specific 
calculations <- 
  filter(exploratory, `% Reached` == 0.0 & month == 7) %>%
  select(fips, total_HH, total_SNAP)

not_covered_SNAP <- sum(calculations$total_SNAP)
view(not_covered_SNAP)

# To get the denominator for % not covered
calculations2 <-
  filter(exploratory, month == 7) %>%
  select(fips, total_HH, total_SNAP)

sum(calculations2$total_SNAP)

not_covered_SNAP/sum(calculations2$total_SNAP)

# General Population, not just SNAP
not_covered_general <- sum(calculations$total_HH)
view(not_covered_general)

sum(calculations2$total_HH)

not_covered_general/sum(calculations2$total_HH)

```

# Overall SNAP Coverage in State and %'s Reached

```{r}
sum(amz_wmt_reach$`Total Reached`)

sum(amz_wmt_reach$`Total Reached`)/sum(calculations2$total_SNAP)

sum(amz_wmt_reach$`Reached by Walmart`)

sum(amz_wmt_reach$`Reached by Walmart`)/sum(calculations2$total_SNAP)

sum(amz_wmt_reach$`Reached by Amazon`)
sum(amz_wmt_reach$`Reached by Amazon`)/sum(calculations2$total_SNAP)

```




```{r}

# Graph of % SNAP users reached vs. % county on SNAP

ggplot(amz_wmt_reach, aes(x =`SNAP Concentration`, y = `% Reached`)) +
  geom_point(shape = 1)

# Graph of % SNAP users reached vs. COVID Cases FOR SPECIFIC MONTH

exploratory %>%
  filter(month == "9") %>%
  ggplot(aes(x = cases_perPop, y = `% Reached`)) +
  geom_point(shape = 1)

```



## Layer in Sam's Mapping of Coverage by Amazon & Walmart

# recreate Sam's work for creating inital shape files (https://github.com/unbox-initative/data/blob/master/eda/sam_shopping_dashboard.Rmd)

```{r}

ca_zip <-
  ca_zip %>%
  #st_transform(crs=4326)
  st_as_sf(crs = 4326)

CA_ALBERS <- 
  "+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

# amazon + walmart reach - all of CA
az <- 
  read.csv("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data-raw/amazonfresh_zipcodes.csv",colClasses=c("character","character")) %>% 
  # filter(Zip %in% bay_zip$ZIP_CODE) %>%
  # left_join(bay_zip, by=c("Zip"="ZIP_CODE")) %>%
  left_join(ca_zip, by=c("Zip"="ZIP_CODE")) %>%
  st_as_sf(crs=4326) %>% 
  mutate(area = st_area(.)) %>% 
  summarise(area=sum(area))
# 
# ggplot() +
#   geom_sf(data = az)

w <- 
  read.csv("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data-raw/walmart_delivery_stores_ca.csv") %>% 
  # filter(Zip.Code %in% bay_zip$ZIP_CODE) %>% 
  st_as_sf(coords=c("Longitude", "Latitude"), crs=4326)

# ggplot()+
#   geom_sf(data = w) 

wz <- 
  w %>% 
  st_transform(crs = CA_ALBERS) %>% 
  st_buffer(dist = 9 * 1609.344) %>% 
  st_transform(crs=4326) %>% 
  #st_intersection(bay_zip) %>%
  st_intersection(ca_zip) %>%
  mutate(area = st_area(.)) %>% 
  summarise(area=sum(area))

# ggplot() +
#   geom_sf(data = wz)

```


## Map Overlay of Amazon & Walmart with Heat Map w COVID Cases

```{r}

df_allVar %>%
  st_as_sf() %>%  
  filter(month == 6) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +
  geom_sf(data = wz, color = "orange") +
  geom_sf(data = w, color = "yellow") +
  geom_sf(data = az, color = "blue") +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.4,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, .96),
    plot.title = element_text(hjust = .5, vjust = 2.5),
    plot.subtitle = element_text(hjust = 2, vjust = 1.5)
  ) +
  labs(
    title = "SNAP OPP Coverage & COVID Cases (% of Population), June 2020",
    caption = "Data source: New York Times Coronavirus Cases US"
  )

```


# Calculation for Top 5 Counties Hardest Hit by COVID and Coverage for SNAP OPP Users

```{r}

df_allVar_hardest <-
  df_allVar %>%
  filter(month == 6)

exploratory_june_total <-
  exploratory %>%
  select(`Total Reached`, `% Reached`, NAME, month, total_pop, total_SNAP, fips) %>%
  filter(month == 6) %>%
  filter(fips == 6037 | fips == 6065 | fips == 6073 | fips == 6059 | fips == 6071) 

  sum(exploratory_june_total$`Total Reached`)


sum(exploratory_june_total$`Total Reached`)/sum(exploratory_june_total$total_SNAP)

exploratory_june_perPerson <-
  exploratory %>%
  select(`Total Reached`, `% Reached`, NAME, month, total_pop, total_SNAP, fips) %>%
  filter(month == 6) %>%
  filter(fips == 6025 | fips == 6031 | fips == 6037 | fips == 6107 | fips == 6065) 

  sum(exploratory_june_perPerson$`Total Reached`)

sum(exploratory_june_perPerson$`Total Reached`)/sum(exploratory_june_perPerson$total_SNAP)

exploratory_july_perPerson <-
  exploratory %>%
  select(`Total Reached`, `% Reached`, NAME, month, total_pop, total_SNAP, fips) %>%
  filter(month == 7) %>%
  filter(fips == 6025 | fips == 6031 | fips == 6037 | fips == 6041 | fips == 6107) 

  sum(exploratory_july_perPerson$`Total Reached`)

sum(exploratory_july_perPerson$`Total Reached`)/sum(exploratory_july_perPerson$total_SNAP)


exploratory_august_perPerson <-
  exploratory %>%
  select(`Total Reached`, `% Reached`, NAME, month, total_pop, total_SNAP, fips) %>%
  filter(month == 8) %>%
  filter(fips == 6025 | fips == 6031 | fips == 6029 | fips == 6107 | fips == 6047) 

  sum(exploratory_august_perPerson$`Total Reached`)

sum(exploratory_august_perPerson$`Total Reached`)/sum(exploratory_august_perPerson$total_SNAP)
  

```




# Overlay Coverage and SNAP % per county

```{r}

# Map for SNAP Usage & Coverage Overlay
df_allVar %>%
  st_as_sf() %>%  
  ggplot() +
  geom_sf(aes(fill = percentSnap), color = "grey25", size = 0.1) +
  geom_sf(data = wz, color = "orange") +
  geom_sf(data = w, color = "yellow") +
  geom_sf(data = az, color = "blue") +
  
  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population on SNAP & SNAP OPP Coverage",
    caption = "Source: ACS 2019 Census Data"
  )


```

# SNAP OPP Overlap with Internet and Computer Access

```{r}


# Map for No Internet

df_allVar %>%
  st_as_sf() %>%  
  ggplot() +
  geom_sf(aes(fill = percentNoInternet), color = "grey25", size = 0.1) +
  geom_sf(data = wz, color = "orange") +
  geom_sf(data = w, color = "yellow") +
  geom_sf(data = az, color = "blue") +
  
  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Internet & SNAP OPP Coverage",
    caption = "Source: ACS 2019 Census Data"
  )

# Map for No Computer

df_allVar %>%
  st_as_sf() %>%  
  ggplot() +
  geom_sf(aes(fill = percentNoComp), color = "grey25", size = 0.1) +
  geom_sf(data = wz, color = "orange") +
  geom_sf(data = w, color = "yellow") +
  geom_sf(data = az, color = "blue") +
  
  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Computer & SNAP OPP Coverage",
    caption = "Source: ACS 2019 Census Data"
  )


```

# Data Analysis for Computer & Internet Access

```{r}

digital_analysis <-
  amz_wmt_reach %>%
    left_join(ca_counties %>% select(NAME, fips), by = "NAME")

digital_analysis <-
  digital_analysis %>%
  left_join(df_allVar2 %>% select(fips, cases_perPop, month, total_pop, total_SNAP, percentBroadband, percentNoInternet, percentNoComp, percentDialUp), by = "fips") %>%
  # for broadband:
  # filter(fips == 6041 | fips == 6075 | fips == 6027 | fips == 6063 | fips == 6093) %>%
  # for No Internet:
  # filter(fips == 6105 | fips == 6049 | fips == 6091 | fips == 6043 | fips == 6021) %>%
  # for No Computer Access
  #filter(fips == 6049 | fips == 6105 | fips == 6091 | fips == 6043 | fips == 6093) %>%
  # for Has Dial Up
  filter(fips == 6003 | fips == 6043 | fips == 6009 | fips == 6105 | fips == 6093) %>%
  filter(month == 7)

sum(digital_analysis$`Total Reached`)

sum(digital_analysis$`Total Reached`)/sum(digital_analysis$total_SNAP)

sum(digital_analysis$total_SNAP)

```

# Data Analysis for Race/Ethnicity

```{r}

demo_analysis <-
  amz_wmt_reach %>%
  left_join(ca_counties %>% select(NAME, fips), by = "NAME")

demo_analysis <-
  demo_analysis %>%
  left_join(df_allVar2 %>% select(fips, cases_perPop, month, total_pop, total_SNAP, percentWhite, percentBlack, percentNative, percentAsian, percentHaw_PacI, percentOther, percentTwoMore, percent_Latino), by = "fips") %>%
  filter(month == 7) %>%
  # For White
  # filter(NAME == "Sierra" | NAME == "Nevada" | NAME == "Calaveras" | NAME == "Plumas" | NAME == "Modoc")
  # For Black
  # filter(NAME == "Solano" | NAME == "Alameda" | NAME == "Sacramento" | NAME == "Contra Costa" | NAME == "Lassen")
  # For Native
  # filter(NAME == "Alpine" | NAME == "Inyo" | NAME == "Del Norte" | NAME == "Trinity" | NAME == "Humboldt")
  # for For Asian
  # filter(NAME == "Santa Clara" | NAME == "San Francisco" | NAME == "Alameda" | NAME == "San Mateo" | NAME == "Orange")
  # For HI/Pac Islander 
   # filter(NAME == "San Mateo" | NAME == "Sacramento" | NAME == "Solano" | NAME == "Alameda" | NAME == "Lassen")
  # For Latino
   filter(NAME == "Imperial" | NAME == "Tulare" | NAME == "San Benito" | NAME == "Merced" | NAME == "Colusa")

sum(demo_analysis$`Total Reached`)
sum(demo_analysis$total_SNAP)

sum(demo_analysis$`Total Reached`)/sum(demo_analysis$total_SNAP)


```

# Data Analysis for Transportation Method

```{r}

transp_analysis <-
  amz_wmt_reach %>%
  left_join(ca_counties %>% select(NAME, fips), by = "NAME")

transp_analysis <-
  transp_analysis %>%
  left_join(df_allVar2 %>% select(fips, cases_perPop, month, total_pop, total_SNAP, percent_trans_vehicle, percentTransPublic, percentTransBike, percentTransWalk, percentTransOther, percentTransHome), by = "fips") %>%
  filter(month == 7) %>%
  # Vehicle
  # filter(NAME == "San Benito" | NAME == "Orange"| NAME == "Ventura"| NAME == "Sonoma"| NAME == "Santa Clara")
  # Public Transport
  filter(NAME == "San Francisco" | NAME == "Mono"| NAME == "Alameda"| NAME == "San Mateo"| NAME == "Contra Costa")


sum(transp_analysis$`Total Reached`)
sum(transp_analysis$total_SNAP)
sum(transp_analysis$`Total Reached`)/sum(transp_analysis$total_SNAP)

```



# Integrating in Sam's Food Desert Analysis (copied from Sam's code:
# https://github.com/unbox-initative/dashboard/blob/master/eda/sam_shopping_dashboard.Rmd)


```{r}

ca_desert_shape <- readRDS("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/ca_desert_shape.rds")

desert_reach <- 
  amz_wmt_zip$amz_zip %>% 
  st_union(amz_wmt_zip$wmt_zip) %>% 
  st_intersection(st_make_valid(ca_desert_shape)) %>% 
  mutate(
    leftover_area = st_area(.),
    area_proportion = leftover_area / og_area, # proportion of people served in food-desert-classified areas
    snap_reached = area_proportion * SNAP
  ) %>% 
  st_collection_extract(type = c("POLYGON"), warn = FALSE)
desert_noreach <- 
  ca_desert_shape %>% 
  st_make_valid() %>% 
  st_difference(amz_wmt_zip$amz_zip %>% st_union(amz_wmt_zip$wmt_zip)) %>% 
  st_collection_extract(type = c("POLYGON"), warn = FALSE)
leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(
    data = desert_reach,
    color = "#56bedf",
    fillOpacity = 0.5,
    weight = 1,
    label = ~snap_reached
  ) %>%
  addPolygons(
    data = desert_noreach,
    color = "#e851a2",
    fillOpacity = 0.5,
    weight = 1,
    label = ~SNAP
  )

```


```{r}

# snap_cbg_tract <- 
#   map_dfr(
#     ca_counties$COUNTYFP, 
#     function(x) {
#       getCensus(name = "acs/acs5",
#                 vintage = 2019,
#                 vars = c("B19058_002E"), 
#                 region = "block group:*", 
#                 regionin = paste0("state:06+county:", x)) %>% 
#         mutate(
#           GEOID = paste0(state, county, tract, block_group),
#           tract = paste0(state, county, tract)
#         ) %>% 
#         select_if(
#           !names(.) %in% c("state", "county", "block_group")
#         ) %>% 
#         rename("SNAP" = "B19058_002E")
#     }) %>% 
#   left_join(ca_cbgs %>% select(GEOID))
# 
# 
# snap_cbg_tract %>% 
#   filter(tract %in% ca_food_desert$CensusTract) %>%
#   st_as_sf() %>%
#   st_transform(crs = 4326) %>% 
#   mutate(og_area = st_area(.)) %>% 
#   saveRDS("rds/ca_desert_shape.rds")


# total snap reached in food deserts
round(sum(desert_reach$snap_reached))
sum(desert_reach$snap_reached) / sum(ca_desert_shape$SNAP)
# total snap not reached in food deserts
round(sum(ca_desert_shape$SNAP) - as.numeric(sum(desert_reach$snap_reached)))
(sum(ca_desert_shape$SNAP) - as.numeric(sum(desert_reach$snap_reached))) / sum(ca_desert_shape$SNAP)


#saveRDS(desert_reach, "rds/desert_reach.rds")
#saveRDS(desert_noreach, "rds/desert_noreach.rds")

```





## another work around method to try to re-create Sam's shapefiles

```{r}

longlat <- "+proj=longlat +datum=WGS84 +no_defs"


ca_walmart <-
  amz_wmt_zip$wmt_zip %>%
  st_as_sf(crs = longlat) 
  #st_transform(crs = st_crs(4326))
  #read_sf(dsn = "covid-19-data/data/amz_wmt_zip.rds") %>%
  #st_cast("MULTIPOLYGON")
  #amz_wmt_zip$wmt_zip %>%
  #st_transform(crs = longlat)
  ca_walmart %>%
    #st_transform(crs =4326) %>%
   #st_cast("MULTIPOLYGON") %>%
    #st_transform(crs = longlat) %>%
    ggplot() +
    geom_sf()
 # mapview(ca_walmart)
  
# 
# list_files <- readRDS("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/amz_wmt_zip.rds")
# amz_zip <- list_files$amz_zip
# wmt_zip <- list_files$wmt_zip
# wmt <- list_files$wmt
amz_zip %>%
  ggplot() +
  geom_sf()
test <- unlist(amz_zip$geometry)

# Code from Nico:
# separated_coord <- amz_zip %>%
#     mutate(lat = unlist(amz_zip$geometry,1),
#            long = unlist(amz_zip$geometry,2))
  
ca_walmart <-
  ca_walmart %>%
  st_cast("MULTIPOLYGON") %>%
  st_transform(crs = longlat)
  
  
ca_amazon <-
  amz_wmt_zip$amz_zip %>%
  st_transform(crs = 4326)

ca_walmart_zip <-
  amz_wmt_zip$wmt_zip


# df_1 <- amz_wmt_zip$amz_zip
# df_1 %>% 
#   leaflet() %>%
#   addProviderTiles(providers$CartoDB.Positron) %>%
#   addPolygons() %>%
#   addPolygons(
#     data= df_allVar2 %>% st_as_sf,
#     fillColor = ~total
#   )

  

```

# Try Leaflet Option with Sam (copied code from https://github.com/unbox-initative/data/blob/master/baymap/global.R)

```{r}

longlat <- "+proj=longlat +datum=WGS84 +no_defs"

map_amz_wmt <- 
  leaflet() %>% 
    addProviderTiles(providers$CartoDB.Positron) %>%
    addPolygons(
      data = ca_walmart ,
      color = "#e851a2",
      fillOpacity = 0.5,
      weight=1,
      group="Amazon"
    )




```




# Create Scatterplot per Bill's Suggestion- % Reached and COVID Cases

```{r}

#Create DF with Amazon and Walmart Reach and COVID Cases
ca_data <- 
  ca_data %>%
  rename(County = "county")

store_reach_covid <-
  amz_wmt_reach %>%
  left_join(
    ca_data %>%
      # rename(County = 'county') %>% 
      mutate(month = lubridate::floor_date(date, unit = "month")) %>%
      group_by(County, month) %>%
      #filter(month == 7) %>% 
      summarise((total = sum(cases))), 
    by = "County"
  )
    
# Multi-dimensional Plot
ggplot(store_reach_covid) +
  geom_point(aes(month, `SNAP Concentration`, size = `(total = sum(cases))`, color =
                   County)) +
  theme_light()+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  scale_x_date(date_labels = "%d-%b", date_breaks = "1 month")+
  ggtitle("testing")+
  xlab("Month")
  




# df <-
#   df %>%
#   left_join(ca_counties, by = "fips")
# 
# 
#   df <- 
#   ca_data %>% 
#   select(date, fips, cases, deaths) %>%
#   mutate(cases = as.integer(cases)) %>%
#   mutate(
#     date = as.Date(date), 
#     month = month(date)
#   ) %>%
#   group_by(fips, month) %>%
#   summarise(total = sum(cases))
#   
#   
#   ca_cases <-
# #   ca_counties %>%
# #   left_join(
# #     ca_data %>%
# #       mutate(month = lubridate::floor_date(date, unit = "month")) %>%
# #       group_by(fips, month) %>% 
# #       summarize(total = sum(cases)) %>%
# #       ungroup() %>%
# #       left_join(ca_pop, by = "fips") %>%
# #       mutate(cases_per_capita = total / pop),
# #     by = "fips"
# #   )


```



# Create plot comparing % OPP Reach v % Population on SNAP
```{r}


ggplot(amz_wmt_reach) +
  geom_point(aes(`SNAP Concentration`, `% Reached`)) +
  
  theme_light()+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  ggtitle("Reach of SNAP OPP vs. % Population on SNAP")+
  xlab("Percent County Population on SNAP")



```





## NOTES & REFERNCE: Example code from Nico
```{r}
# ggplot() +
#   geom_sf(aes(fill = ca_data$cases), data = ca, colour = "white")
# 
# counties %>% 
#   left_join(election_2012_2016, by = c("NAME" = "county_name")) %>%
#   ggplot() +
#   geom_sf(aes(fill = r_d_change), size = 0.01) +
#   geom_sf(data = counties, color = "grey25", fill = NA, size = 0.2) +
#   scale_fill_gradient2(
#     #low = COLOR_LOW,
#    # high = COLOR_HIGH,
#     na.value = "grey"
#   ) +
#   guides(
#     fill =
#       guide_colorbar(
#         barheight = 0.5,
#         barwidth = 15,
#         title = NULL
#       )
#   ) +
#   theme_void() +
#   theme(
#     legend.direction = "horizontal",
#     legend.position = c(0.5, 0.95),
#     plot.title = element_text(hjust = 0.5),
#     plot.subtitle = element_text(hjust = 0.5)
#   ) +
#   labs(
#     title = "TITLE HERE",
#     caption = "Source: New York Times Coronavirus Cases US"
#   )

```

