---
title: "ca_map"
output: html_document

#references: https://rdrr.io/cran/tigris/man/counties.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown is for the purposes of generating a map of CA.
```{r echo=FALSE}
# Libraries
library(tidyverse)
library(tidycensus)
library(leaflet)
library(leaflet.extras)
library(urbnmapr)
library(dplyr)
library(sf)
library(maps)
library(tigris)
library(ggplot2)
library(lubridate)
library(RColorBrewer)
library(ussf)

# PARAMETERS

# Read in Files and Data

file_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/ca-data.rds") 
amz_wmt_zip_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/amz_wmt_zip.rds") 
amz_wmt_reach_in <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data/amz_wmt_reach.rds") 
ruccodes <- ("/Users/isabellefoster/GitHub/isaFos/Amazon_Walmart/covid-19-data/data-raw/ruralurbancodes2013-3.csv")

#Colors

COLOR_LOW = "darkorchid1"
COLOR_HIGH = "darkorchid4"
```

# Read in Data

```{r}
ca_data <- 
  read_rds(file_in) %>%
  mutate(fips = as.integer(fips))
amz_wmt_zip <- read_rds(amz_wmt_zip_in)
amz_wmt_reach <- read_rds(amz_wmt_reach_in)
ruc_codes <- read_csv(ruccodes)

```

# Read in Geometry Shape File

```{r}
ca_counties <- 
  ussf::boundaries(
    geography = "county",
    resolution = "5m", 
    projection = "longlat"
  ) %>%
  filter(as.integer(STATEFP) == 06) %>%
  mutate(fips = as.integer(GEOID))
  
```

## Create Column for Number of Cases, by Month

```{r}
df <- 
  ca_data %>% 
  select(date, fips, cases, deaths) %>%
  mutate(cases = as.integer(cases)) %>%
  mutate(
    date = as.Date(date), 
    month = month(date)
  ) %>%
  group_by(fips, month) %>%
  summarise(total = sum(cases))

```

# Work with Bill
#Imp. note to create a floor on the date, so that there aren't duplicate years
```{r}
# ca_cases <-
#   ca_counties %>%
#   left_join(
#     ca_data %>%
#       mutate(month = lubridate::floor_date(date, unit = "month")) %>%
#       group_by(fips, month) %>% 
#       summarize(total = sum(cases)) %>%
#       ungroup() %>%
#       left_join(ca_pop, by = "fips") %>%
#       mutate(cases_per_capita = total / pop),
#     by = "fips"
#   )
# 
# ca_walmart <-
#   amz_wmt_zip$wmt_zip %>%
#   st_as_sf() %>%
#   st_transform(crs = st_crs(4326))
# 
# ca_amazon <-
#   amz_wmt_zip$amz_zip %>%
#   st_transform(crs = 4326)
```


##ggplot with Bill
```{r}

# ggplot() +
#   #geom_sf(aes(fill = cases_per_capita), data = ca_cases) +
#  # geom_sf(aes(fill = area), data = st_as_sf(amz_wmt_zip$wmt_zip)) 
#   geom_sf(data = amz_wmt_zip$wmt, color = "red")

```


# Create Fips Variable for ca_counties

```{r}

ca_counties <-
  ca_counties %>%
  mutate(fips = as.integer(GEOID))

```

# Join Data Sets

```{r}

df <-
  df %>%
  left_join(ca_counties, by = "fips")

```


## Get County Data from Census Data 

```{r}

census_ca <-
  load_variables(year = 2018, dataset ="acs5")

vars_acs5 <-
  c(
    total_pop = "B01003_001",
    total_SNAP = "B19058_002",
    total_white = "B02001_002",
    total_black = "B02001_003",
    total_nativeAlaska_AmInd = "B02001_004",
    total_asian = "B02001_005",
    total_Haw_PacIs = "B02001_006",
    total_other = "B02001_007",
    total_twoMore = "B02001_008",
    has_comp = "B28003_002",
    has_comp_dialUp = "B28003_003",
    has_comp_broadband = "B28003_004",
    has_comp_noInternet = "B28003_005",
    no_comp = "B28003_006",
    workTransVehicle = "B08301_001",
    workTransPublicTrans = "B08301_010",
    workTrans_bike = "B08301_018",
    workTrans_walk = "B08301_019",
    workTrans_other = "B08301_020",
    workTrans_workHome = "B08301_021"
  )

df_acs5 <-
  get_acs(
    geography = "county",
    variables = vars_acs5,
    year = 2018,
    state = 06
  )

# ##added with Bill 
# ca_pop <-
#   get_acs(
#     geography = "county",
#     variables = "B01003_001",
#     year = 2018,
#     state = 06
#   ) %>%
#   transmute(
#     fips = as.integer(GEOID),
#     pop = estimate
#   )


```

## Join Census Data to COVID data, using FIPS

```{r}

# Create FIPS variable in ACS data frame

df_acs5 <-
  df_acs5 %>%
    mutate(
      fips = as.integer(GEOID)
    )

# Left join data COVID data set and create new variables per population count

df_allVar <-
  df %>%
  left_join(df_acs5, by = "fips") %>%
  select(-moe) %>%
  #ungroup() %>% 
  pivot_wider(
    names_from = variable,
    values_from = estimate
  ) %>%
  mutate(
    cases_perPop = (total / total_pop),
    percentWhite = (total_white / total_pop),
    percentBlack = (total_black / total_pop),
    percentNative = (total_nativeAlaska_AmInd / total_pop),
    percentAsian = (total_asian / total_pop),
    percentHaw_PacI = (total_Haw_PacIs / total_pop),
    percentOther = (total_other / total_pop),
    percentTwoMore = (total_twoMore / total_pop),
    percent_trans_vehicle = (workTrans_vehicle / total_pop),
    percentTransPublic = (workTrans_publicTrans /total_pop),
    percentTransBike = (workTrans_bike / total_pop),
    percentTransWalk = (workTrans_walk / total_pop),
    percentTransOther = (workTrans_other / total_pop),
    percentTransHome = (workTrans_workHome / total_pop),
    percentSnap = (total_SNAP / total_pop),
    percentComp = (has_comp / total_pop),
    percentDialUp = (has_comp_dialUp / total_pop),
    percentBroadband = (has_comp_broadband /total_pop),
    percentNoInternet = (has_comp_noInternet /total_pop),
    percentNoComp = (no_comp / total_pop)
  )
 

```


# Read RUC Code Data as numberics

```{r}
ruc_codes 
  ruc_codes$FIPS <- as.numeric(ruc_codes$FIPS)
  ruc_codes$RUCC_2013 <- as.numeric(ruc_codes$RUCC_2013)
 

```


# Join RUC Code Data --NEED TO FIX
```{r}
ruc_codes_new <- 
ruc_codes %>%
  rename(
    fips = FIPS
  )

df_allVar2 <-
  df_allVar %>%
    left_join(ruc_codes_new, by = "fips")

```


## Create Plot of CA
## Used this site as reference: https://rdrr.io/cran/tigris/man/counties.html

```{r}
ca <- counties("California", cb = TRUE)

gg <- ggplot()
gg <- gg + geom_sf(data = ca, color="black", fill="white", size=0.25)

gg
```


## Create HeatMap of CA with Total Number of COVID Cases for the Month of July 2020

```{r}

df %>% 
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = total), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Total COVID CA Cases Per Month, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )

# df %>%
#   filter(month==7) %>%
#   View()

```

## Create Heat Map of CA with Cases Count per Population for July 2020

```{r}

 df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )



```

```{r}
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )

```



## Map with Sam Overlap

```{r}
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "CA COVID Cases, Percent of Population, July 2020",
    caption = "Source: New York Times Coronavirus Cases US"
  )



```



## Create Heat Maps of CA for Transportation
```{r}

# Map for Vehicle as Main Transportation Form
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percent_trans_vehicle), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Transportion to Work, Vehicle",
    caption = "Source: ACS 2018 Census Data"
  )

# Map for Public Transport as Main Transportation Form
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = workTrans_publicTrans), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Transportion to Work, Public Transit",
    caption = "Source: ACS 2018 Census Data"
  )

```

## Map for SNAP Usage

```{r}

# Map for SNAP Usage
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentSnap), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population on SNAP",
    caption = "Source: ACS 2018 Census Data"
  )
```

## Map of Computer Usage & Internet Access

```{r}

# Map for Computer Access
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentComp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Computer Access",
    caption = "Source: ACS 2018 Census Data"
  )

# Map for Dial Up

df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentDialUp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Dial Up",
    caption = "Source: ACS 2018 Census Data"
  )


# Map for Broadband
df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentBroadband), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population With Broadband",
    caption = "Source: ACS 2018 Census Data"
  )

```


## Map of No Internet / No Computer Access

```{r}

# Map for No Internet

df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentNoInternet), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Internet",
    caption = "Source: ACS 2018 Census Data"
  )

# Map for No Computer

df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = percentNoComp), color = "grey25", size = 0.1) +

  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Percent of Population Without Computer",
    caption = "Source: ACS 2018 Census Data"
  )




```

## Layer in Sam's Mapping of Coverage by Amazon & Walmart

```{r}

# df_1 <- amz_wmt_zip$amz_zip
# df_1 %>% 
#   leaflet() %>%
#   addProviderTiles(providers$CartoDB.Positron) %>%
#   addPolygons() %>%
#   addPolygons(
#     data= df_allVar2 %>% st_as_sf,
#     fillColor = ~total
#   )

  

 df_allVar %>%
  st_as_sf() %>%  
  filter(month == 7) %>% 
  ggplot() +
  geom_sf(aes(fill = cases_perPop), color = "grey25", size = 0.1) +
  geom_sf(aes(fill = amz_wmt_zip$amz_zip), color = "grey25", size = 0.1) +
  geom_sf(aes(fill = amz_wmt_zip$wmt), color = "grey25", size = 0.1) +
  geom_sf(aes(fill = amz_wmt_zip$wmt_zip), color = "grey25", size = 0.1) +
  
  
  scale_fill_gradient2(
    breaks = seq(0.0, 1.0, .1),
    low = COLOR_LOW,
    high = COLOR_HIGH,
    na.value = "grey"
  ) +
  guides(
    fill =
      guide_colorbar(
        barheight = 0.5,
        barwidth = 15,
        title = NULL
      )
  ) +
  theme_void() +
  theme(
    legend.direction = "horizontal",
    legend.position = c(0.5, 0.95),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "XX July 2020",
    caption = "Source: XXX"
  )




```









## NOTES & REFERNCE: Example code from Nico
```{r}
# ggplot() +
#   geom_sf(aes(fill = ca_data$cases), data = ca, colour = "white")
# 
# counties %>% 
#   left_join(election_2012_2016, by = c("NAME" = "county_name")) %>%
#   ggplot() +
#   geom_sf(aes(fill = r_d_change), size = 0.01) +
#   geom_sf(data = counties, color = "grey25", fill = NA, size = 0.2) +
#   scale_fill_gradient2(
#     #low = COLOR_LOW,
#    # high = COLOR_HIGH,
#     na.value = "grey"
#   ) +
#   guides(
#     fill =
#       guide_colorbar(
#         barheight = 0.5,
#         barwidth = 15,
#         title = NULL
#       )
#   ) +
#   theme_void() +
#   theme(
#     legend.direction = "horizontal",
#     legend.position = c(0.5, 0.95),
#     plot.title = element_text(hjust = 0.5),
#     plot.subtitle = element_text(hjust = 0.5)
#   ) +
#   labs(
#     title = "TITLE HERE",
#     caption = "Source: New York Times Coronavirus Cases US"
#   )

```

